Constraining the Interiors of Asteroids Through Close Encounters

### 2022-05-11 paper/main.tex
Thresholds added

\begin{table}
  \centering
  \begin{tabular}{lll} \hline
    Encounter property & Strong & Weak \\ \hline
    Excess velocity ($v_\infty$) & & \\
    Perigee ($r_p$) & & \\
    Spin pole uncertainty ($\sigma_\theta$) & & \\
    Spin period uncertainty ($P_\omega \sigma_\rho$) & & \\
    Asteroid length ($a_\mathcal{A}$) & & \\
    Cadence ($\Delta t$) & & \\
    Data gap ($T_\text{gap}$) & & \\
    Rotational period ($P_\omega$) & & \\ \hline
  \end{tabular}
  \caption{For each encounter property discussed in section \ref{sec:discussion}, the cut-offs (i.e., the values which leads to $\sigma(K_{3 m})$ at the threshold value) are given. Properties inside the strong cut-off have all $\sigma(K_{3m})$ under the threshold value, while properties inside the weak cutoff have at least one $\sigma(K_{3m})$ under the threshold value. The reference asymmetric asteroid is used. \jtd{summary}}
  \label{tab:threshold-summary}
\end{table}

@@

\jtd{The failure of this model makes me think we really should only do the finite element analysis. Though it is slow.}

>>>>

\jtd{This Klm uncertainty threshold language is still in the paper, although the numbers in the above table reflect the method I used for the conference, which is asking what encounter properties yield density distributions with uncertainty 100 or 20\% of the local density. The caveat to the latter, density-distribution based, uncertainty threshold is that it changes based on which models you use and how many Klms you choose to fit due to the fact that the density distribution is underdetermined. A constraint on the density moments is more general, but harder to define. My feeling is that we should use this distribution-based constraint, and mention the caveats here. I'll write up all this if Julien agrees.}

\begin{table}
  \centering
  \begin{tabular}{lll} \hline
    Encounter property & $\sigma_\rho / \rho = 100\%$ & $\sigma_\rho / \rho = 20\%$ \\ \hline
    Perigee ($r_p$, Earth radii) & $<$7.9 & $<$4.7 \\
    Spin pole uncertainty ($\sigma_\theta$, $^\circ$) & $<$2.8 & $<$0.5 \\
    Spin period uncertainty ($P_\omega \sigma_\rho$, ms) & $<$15 & $<$3.1\\
    Asteroid length ($a_\mathcal{A}$, m) & $>$180 & $>$1100 \\
    Cadence ($\Delta t$, min) & $<$38 & $<$2 \\
    Data gap ($T_\text{gap}$, hr) & $<$1.8 & $<$0 \\
    Period ($P_\omega$, hr) & $>$4.3 & $>$9.5\\ \hline
  \end{tabular}
  \caption{For each encounter property discussed in section \ref{sec:discussion}, the cut-offs (i.e., the values which leads to $\sigma(K_{3 m})$ at the threshold value) are given. Properties inside the strong cut-off have all $\sigma(K_{3m})$ under the threshold value, while properties inside the weak cut-off have at least one $\sigma(K_{3m})$ under the threshold value. The reference asymmetric asteroid is used. \jtd{summary}}
  \label{tab:threshold-summary}
\end{table}

@@

\jtd{The failure of this model makes me think we really should only do the finite element analysis, though I think uncertainty will only improve if we average over multiple grids. That's based on my messing around so far.}
